The fraction of polar aligned circumbinary disks

### 2025-04-04 src/tex/review.tex
L184

\documentclass{letter}
\usepackage{xcolor}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{amsmath}

@@

>>>>

\documentclass{letter}
\usepackage{xcolor}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{amsmath}
\usepackage{bm}

@@

    \begin{response}
        {L184: Perhaps specify that "isotropic angular momentum distribution" means that the relative angle between the disc and binary orbital planes is uniformly distributed. This would help to give a more clear astrophysical interpretation.}
        This description is not entirely correct. By ``isotropic'' we mean that the specific angular momentum vector $\bm{\ell}$ has no preference towards any infinitesimal solid angle $d\Omega$. We have added text to clarify.
    \end{response}
